Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-24 msr/msr2011.tex
Neil audit this one please:     - [X] 4: "Fig 5a shows func. port. and maint. contain more       labelled topics" -- what are the practical implications?           - reponse: we suggested the practical implications of the opposite,             why is effeciency periodic?             addressed in text.

%\subsection{Timeline analysis}
Figures \ref{fig:mysql-timeline} and \ref{fig:maxdb-timeline} show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to that NFR. For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with that NFR per period 
relative to the maximum number of labelled topics overall. For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labelled topics, since these NFRs have been more intensely shaded.
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.

>>>>

%\subsection{Timeline analysis}
Figures \ref{fig:mysql-timeline} and \ref{fig:maxdb-timeline} show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to that NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with that NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded; 
one interesting stream is \emph{efficiency} which shows periodic
activity, does this suggest that once maybe efficiency related changes
have longer lasting effects?
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.
